Discovering the Rules of language using Bayesian Program Learning

### 2018-05-01 test.tex
textbook solutions

@@

@@

\emph{Latin:}\\\begin{longtable}{lll|l}\toprule
$\varnothing$ $+$stem$+$ \textipa{s} & $\varnothing$ $+$stem$+$ \textipa{is} & $\varnothing$ $+$stem$+$ \textipa{i:} & UR
\\ \midrule
\textipa{arks} & \textipa{arkis} &  --  &  -- \\
\textipa{duks} & \textipa{dukis} &  --  &  -- \\
\textipa{daps} & \textipa{dapis} &  --  &  -- \\
\textipa{re:ks} & \textipa{re:gis} &  --  &  -- \\
\textipa{falanks} & \textipa{falangis} &  --  &  -- \\
\textipa{filiks} & \textipa{filikis} &  --  &  -- \\
\textipa{lapis} & \textipa{lapidis} &  --  &  -- \\
\textipa{li:s} & \textipa{li:tis} &  --  &  -- \\
\textipa{fraws} & \textipa{frawdis} &  --  &  -- \\
\textipa{noks} & \textipa{noktis} &  --  &  -- \\
\textipa{frons} & \textipa{frontis} &  --  &  -- \\
\textipa{frons} & \textipa{frondis} &  --  &  -- \\
\textipa{inku:s} & \textipa{inku:dis} &  --  &  -- \\
\textipa{sors} & \textipa{sortis} &  --  &  -- \\
\textipa{fu:r} & \textipa{fu:ris} &  --  &  -- \\
\textipa{murmur} & \textipa{murmuris} &  --  &  -- \\
\textipa{augur} & \textipa{auguris} &  --  &  -- \\
\textipa{arbor} & \textipa{arboris} &  --  &  -- \\
\textipa{pugil} & \textipa{pugilis} &  --  &  -- \\
\textipa{sal} & \textipa{salis} &  --  &  -- \\
\textipa{adeps} & \textipa{adipis} &  --  &  -- \\
\textipa{apeks} & \textipa{apikis} &  --  &  -- \\
\textipa{pri:nkeps} & \textipa{pri:nkipis} &  --  &  -- \\
\textipa{ekwes} & \textipa{ekwitis} &  --  &  -- \\
\textipa{miles} & \textipa{militis} &  --  &  -- \\
\textipa{no:men} & \textipa{no:minis} &  --  &  -- \\
\textipa{karmen} & \textipa{karminis} &  --  &  -- \\
\textipa{lu:men} & \textipa{lu:minis} &  --  &  -- \\
\textipa{wenter} & \textipa{wentris} &  --  &  -- \\
\textipa{pater} & \textipa{patris} &  --  &  -- \\
\textipa{kada:wer} & \textipa{kada:weris} &  --  &  -- \\
\textipa{tu:ber} & \textipa{tu:beris} &  --  &  -- \\
\textipa{piper} & \textipa{piperis} &  --  &  -- \\
\textipa{karker} & \textipa{karkeris} &  --  &  -- \\
\textipa{die:s} &  --  & \textipa{die:i:} &  -- \\
\textipa{li:ber} &  --  & \textipa{li:beri:} &  -- \\
\textipa{miser} &  --  & \textipa{miseri:} &  -- \\
\textipa{ager} &  --  & \textipa{agri:} &  -- \\
\textipa{sinister} &  --  & \textipa{sinistri:} &  -- \\
\textipa{liber} &  --  & \textipa{libri:} &  -- \\
\textipa{as} & \textipa{assis} &  --  &  -- \\
\textipa{os} & \textipa{ossis} &  --  &  -- \\
\textipa{far} & \textipa{farris} &  --  &  -- \\
\textipa{mel} & \textipa{mellis} &  --  &  -- \\
\textipa{o:s} & \textipa{o:ris} &  --  &  -- \\
\textipa{flo:s} & \textipa{flo:ris} &  --  &  -- \\
\textipa{mu:s} & \textipa{mu:ris} &  --  &  -- \\
\textipa{cru:s} & \textipa{cru:ris} &  --  &  -- \\
\textipa{kinis} & \textipa{kineris} &  --  &  -- \\
\textipa{pulvis} & \textipa{pulveris} &  --  &  -- \\
\bottomrule\end{longtable}
\begin{tabular}{l}\emph{Rules: }\\
\verb|[-sonorant]| $\to$ \verb|[-voice]| /  \verb|_| \verb|[-voice]|\\\textipa{e} $\to$ $2$ /  \verb|_| \verb|[-liquid]| \verb|[+vowel]|\\\verb|[-vowel]| $\to$ $\varnothing$ / \verb|[+coronal]| \verb|_| \#\\\verb|[-sonorant]| $\to$ \textipa{s} /  \verb|_| \#\\$\varnothing$ $\to$ \textipa{e} / \verb|[-sonorant]| \verb|_| \verb|[+voice]| \#\\$\varnothing$ $\to$ $2$ / \verb|[+sibilant]| \verb|_| \verb|[+vowel]| \verb|[-voice]|\\$\varnothing$ $\to$ $1$ / \# \verb|[-coronal]| \verb|[-high]| \verb|_| \verb|[+voice]| \textipa{i}
\end{tabular}

>>>>

\begin{tabular}{l}\emph{Textbook solution rules: }\\
\verb|[+vowel]| $\to$ \verb|[+highTone]| / \verb|[+highTone]| \verb|[-vowel]|* \verb|_| \\\verb|[+vowel]| $\to$ \verb|[-highTone]| /  \verb|_| \verb|[-vowel]|* \verb|[+highTone]|\\$\varnothing$ $\to$ \textipa{a} / \verb|[-vowel]| \verb|_| \verb|[-vowel]| \#\\\textipa{l} $\to$ \textipa{o} /  \verb|_| \#\\\verb|[-sonorant]| $\to$ \verb|[-voice]| /  \verb|_| \verb|[-voice]|

@@

\begin{tabular}{l}\emph{Textbook solution rules: }\\
\verb|[-vowel]| $\to$ \verb|[+palletized]| /  \verb|_| \textipa{i}\\\textipa{o} $\to$ \textipa{e} / \verb|[+palletized]| $+$ \verb|_| \\\verb|[+vowel -low -high]| $\to$ \textipa{i} /  \verb|_| \verb|[-vowel]|* \verb|[-vowel]| \#\\\verb|[-glide -vowel]| $\to$ \verb|[-palletized]| /  \verb|_| \textipa{e}\\\textipa{l} $\to$ \textipa{w} /  \verb|_| \#\\\textipa{v} $\to$ \textipa{w} /  \verb|_| \#

@@

\emph{Latin:}\\\begin{longtable}{lll|l}\toprule
$\varnothing$ $+$stem$+$ \textipa{s} & $\varnothing$ $+$stem$+$ \textipa{is} & $\varnothing$ $+$stem$+$ \textipa{i:} & UR
\textipa{arks} & \textipa{arkis} &  --  &  -- \\
\textipa{duks} & \textipa{dukis} &  --  &  -- \\
\textipa{daps} & \textipa{dapis} &  --  &  -- \\
\textipa{re:ks} & \textipa{re:gis} &  --  &  -- \\
\textipa{falanks} & \textipa{falangis} &  --  &  -- \\
\textipa{filiks} & \textipa{filikis} &  --  &  -- \\
\textipa{lapis} & \textipa{lapidis} &  --  &  -- \\
\textipa{li:s} & \textipa{li:tis} &  --  &  -- \\
\textipa{fraws} & \textipa{frawdis} &  --  &  -- \\
\textipa{noks} & \textipa{noktis} &  --  &  -- \\
\textipa{frons} & \textipa{frontis} &  --  &  -- \\
\textipa{frons} & \textipa{frondis} &  --  &  -- \\
\textipa{inku:s} & \textipa{inku:dis} &  --  &  -- \\
\textipa{sors} & \textipa{sortis} &  --  &  -- \\
\textipa{fu:r} & \textipa{fu:ris} &  --  &  -- \\
\textipa{murmur} & \textipa{murmuris} &  --  &  -- \\
\textipa{augur} & \textipa{auguris} &  --  &  -- \\
\textipa{arbor} & \textipa{arboris} &  --  &  -- \\
\textipa{pugil} & \textipa{pugilis} &  --  &  -- \\
\textipa{sal} & \textipa{salis} &  --  &  -- \\
\textipa{adeps} & \textipa{adipis} &  --  &  -- \\
\textipa{apeks} & \textipa{apikis} &  --  &  -- \\
\textipa{pri:nkeps} & \textipa{pri:nkipis} &  --  &  -- \\
\textipa{ekwes} & \textipa{ekwitis} &  --  &  -- \\
\textipa{miles} & \textipa{militis} &  --  &  -- \\
\textipa{no:men} & \textipa{no:minis} &  --  &  -- \\
\textipa{karmen} & \textipa{karminis} &  --  &  -- \\
\textipa{lu:men} & \textipa{lu:minis} &  --  &  -- \\
\textipa{wenter} & \textipa{wentris} &  --  &  -- \\
\textipa{pater} & \textipa{patris} &  --  &  -- \\
\textipa{kada:wer} & \textipa{kada:weris} &  --  &  -- \\
\textipa{tu:ber} & \textipa{tu:beris} &  --  &  -- \\
\textipa{piper} & \textipa{piperis} &  --  &  -- \\
\textipa{karker} & \textipa{karkeris} &  --  &  -- \\
\textipa{die:s} &  --  & \textipa{die:i:} &  -- \\
\textipa{li:ber} &  --  & \textipa{li:beri:} &  -- \\
\textipa{miser} &  --  & \textipa{miseri:} &  -- \\
\textipa{ager} &  --  & \textipa{agri:} &  -- \\
\textipa{sinister} &  --  & \textipa{sinistri:} &  -- \\
\textipa{liber} &  --  & \textipa{libri:} &  -- \\
\textipa{as} & \textipa{assis} &  --  &  -- \\
\textipa{os} & \textipa{ossis} &  --  &  -- \\
\textipa{far} & \textipa{farris} &  --  &  -- \\
\textipa{mel} & \textipa{mellis} &  --  &  -- \\
\textipa{o:s} & \textipa{o:ris} &  --  &  -- \\
\textipa{flo:s} & \textipa{flo:ris} &  --  &  -- \\
\textipa{mu:s} & \textipa{mu:ris} &  --  &  -- \\
\textipa{cru:s} & \textipa{cru:ris} &  --  &  -- \\
\textipa{kinis} & \textipa{kineris} &  --  &  -- \\
\textipa{pulvis} & \textipa{pulveris} &  --  &  -- \\
\verb|[-sonorant]| $\to$ \verb|[-voice]| /  \verb|_| \verb|[-voice]|\\\textipa{e} $\to$ $2$ /  \verb|_| \verb|[-liquid]| \verb|[+vowel]|\\\verb|[-vowel]| $\to$ $\varnothing$ / \verb|[+coronal]| \verb|_| \#\\\verb|[-sonorant]| $\to$ \textipa{s} /  \verb|_| \#\\$\varnothing$ $\to$ \textipa{e} / \verb|[-sonorant]| \verb|_| \verb|[+voice]| \#\\$\varnothing$ $\to$ $2$ / \verb|[+sibilant]| \verb|_| \verb|[+vowel]| \verb|[-voice]|\\$\varnothing$ $\to$ $1$ / \# \verb|[-coronal]| \verb|[-high]| \verb|_| \verb|[+voice]| \textipa{i}
\begin{tabular}{l}\emph{Textbook solution rules: }\\
\verb|[-sonorant]| $\to$ \verb|[-voice]| /  \verb|_| \verb|[-voice]|\\\textipa{s} $\to$ $\varnothing$ / \verb|[+coronal +sonorant]| \verb|_| \\\verb|[+coronal -sonorant]| $\to$ $\varnothing$ /  \verb|_| \textipa{s}\\\textipa{e} $\to$ \textipa{i} /  \verb|_| \verb|[-vowel]| \verb|[+vowel]|\\$\varnothing$ $\to$ \textipa{e} / \verb|[-vowel]| \verb|_| \verb|[+coronal +sonorant]| \#\\\textipa{s} $\to$ \textipa{r} / \verb|[+vowel]| \verb|_| \verb|[+vowel]|\\\verb|[+vowel -back]| $\to$ \verb|[-high]| /  \verb|_| \textipa{r}\\$1$ $\to$ $\varnothing$ /  \verb|_| \verb|[-vowel]| \#
